\vspace{5em}On Evaluating Adversarial Robustness

### 2021-04-16 paper.tex
Fixed minor grammatical issue

\subsubsection{Adversarial capabilities}
In order to build meaningful defenses, we need to impose reasonable constraints to the attacker.
%
An unconstrained attacker who wished to cause harm may, for example,
cause bit-flips on the
weights of the neural network, cause errors in the data processing pipeline,
backdoor the machine learning model, or (perhaps more relevant) introduce
large perturbations to an image that would alter its semantics.
%
Since such attacks are outside the scope of defenses adversarial examples,
restricting the adversary is necessary for designing defenses that are
not trivially bypassed by unconstrained adversaries.

>>>>

\subsubsection{Adversarial capabilities}
In order to build meaningful defenses, we need to impose reasonable constraints to the attacker.
%
An unconstrained attacker who wished to cause harm may, for example,
cause bit-flips on the
weights of the neural network, cause errors in the data processing pipeline,
backdoor the machine learning model, or (perhaps more relevant) introduce
large perturbations to an image that would alter its semantics.
%
Since such attacks are outside the scope of defenses to adversarial examples,
restricting the adversary is necessary for designing defenses that are
not trivially bypassed by unconstrained adversaries.
